Non over-massive black holes in early-type galaxies with intermediate-scale discs

### 2015-10-16 papers/ellicular/ellicular.tex
grampians

\title[Ellicular galaxies]{Ellicular galaxies and their (non over-massive) black holes}

@@

\begin{abstract}
The classification ``early-type'' galaxy includes both elliptically- and lenticular-shaped galaxies, 
with the latter composed of a spheroidal stellar system encased within a larger, but flatter, stellar disc. 
Theoretically, the spheroid-to-disc flux ratio can assume any positive value,  
but in practice studies often consider only spheroid/disc decompositions 
in which the disc neatly dominates over the spheroid at large galaxy radii, 
creating an inner ``bulge'' as observed in most spiral galaxies. 
Here we reveal that decompositions in which the disc remains embedded within the spheroid, labelled by some as ``unphysical'',  
correctly reproduce both the photometric and kinematic properties of a class of early-type galaxy 
intermediate between that of elliptical and lenticular galaxies, which we refer to as \emph{ellicular} galaxies for ease of reference. 
Ellicular galaxies have often been confused with lenticular galaxies, 
such that their spheroid luminosities have been considerably underestimated. 
This has recently led to some surprising conclusions, 
such as the claim that a number of ellicular galaxies (e.g.~Mrk 1216, NGC 1277, NGC 1271, and NGC 1332) 
host a central black hole whose mass is abnormally large compared to expectations from the (underestimated) spheroid luminosity. 
We show that when ellicular galaxies are correctly modelled, 
they no longer appear as extreme outliers in the (black hole mass)-(spheroid mass) diagram. 
This not only nullifies the need for invoking different evolutionary scenarios for these galaxies 
but it strengthens the significance of the observed (black hole mass)-(spheroid mass) correlation 
and confirms its importance as a fundamental ingredient for theoretical and semi-analytic models 
used to describe the coevolution of spheroids and their central supermassive black holes.

@@

\begin{keywords}
galaxies: classification -- galaxies: bulges -- galaxies: elliptical and lenticular, 
cD -- galaxies: evolution -- galaxies: structure -- galaxies: individual: Mrk 1216, NGC 1271, NGC 1277, NGC 1332, NGC 4291
\end{keywords}

@@

There are currently two well-known types of stellar discs in galaxies. 
The first are the large-scale discs (with exponential scale lengths of a few kiloparsec) 
that dominate the light at large radii in spiral and lenticular galaxies; 
the second are the small (tens to a couple of hundred parsec) nuclear discs observed in both early- and late-type galaxies 
(e.g.~\citealt{scorzavandenbosch1998,rest2001,balcells2007,ledo2010}). 
The origin of the nuclear discs has been speculated to arise from the infall of small satellite galaxies or gas clouds.  
The origin, or at least the on-going feeding and growth, of the large-scale discs has been attributed to cold gas flows, 
gas rich mergers and halo accretion events 
(e.g.~\citealt{whiterees1978,whitefrenk1991,navarrobenz1991,barneshernquist1992,khochfarsilk2006,dekel2009nat,ceverino2010,
ceverino2012,conselice2012,rubin2012,martini2013,ueda2014}), 
and a thorough review can be found in \citet{combes2014arX,combes2014pro}.
On the other hand, intermediate-sized discs have not received the same level of attention 
as their nuclear and large-scale homologues and 
they have at times been labelled and rejected as ''unphysical'' when detected. 
Here we focus on the increasingly overlooked occurence of intermediate-scale discs in galaxies with directly measured black hole masses. 
The majority of stellar discs have some level of inclination with respect to our line-of-sight, 
and this makes them appear elliptical (rather than round) when seen in projection on the sky. 
This can help one distinguish them from the more spherically-shaped spheroids. 
Identifying the radial extent of these discs with respect to the spheroid can however be subtle. 
Two-dimensional kinematic maps represent an important diagnostic tool for this purpose. 
Most early-type galaxies are classified as ``central fast rotators'' \citep{franx1989,atlas3dIII,scott2014}, 

@@

However, more extended kinematic maps \citep{arnold2014} reveal that 
some of the central fast rotators continue to be fast rotating at large radii, 
whereas other central fast rotators become slow rotators in their outer regions.

@@

($\epsilon = 1 - b/a$, where $b/a$ is the ratio of minor-to-major axis length) of 
(i) a ``lenticular'' galaxy comprised of a large-scale disc which dominates the light at large radii over a relatively smaller encased bulge, 
(ii) an ``elliptical'' galaxy with an additional nuclear stellar disc, 
and (iii) a galaxy composed of an intermediate-scale disc embedded in a relatively larger spheroid 
which dominates the light at large radii. 
We refer to the last case as an ``ellicular'' galaxy. 

@@

The awareness that many so-called ``elliptical'' galaxies actually contain stellar discs 
dates back many years 
\citep{michard1984,djorgovski1985,carter1987,capaccioli1987,capaccioli1988,franx1989,nieto1988,nieto1991,rixwhite1990,rixwhite1992,
vandenbergh1990,bender1990,scorzabender1990,scorzabender1995,
simienmichard1990,cinzanovandermarel1993,donofrio1995,graham1998fornax,scorza1998,scorzavandenbosch1998,bendersaglia1999} and, 
more recently, intermediate-scale discs were anything but unfamiliar to \cite{kormendybender2012} and \cite{krajnovic2013etal}. 
However, the class of ellicular galaxies has been missed by many galaxy modellers of late, 

@@

(e.g.~\citealt{gadotti2008,head2014,querejeta2015,mendezabreu2015}). 
In this paper we investigate the influence this has had on research pertaining to supermassive black hole mass scaling relations involving the host spheroid. \\

@@

In Section \ref{sec:gal} we present a detailed photometric analysis of three ellicular galaxies (Mrk 1216, NGC 1332, and NGC 3115) 
and we briefly describe another five ellicular galaxies (NGC 821, NGC 1271, NGC 1277, NGC 3377, and NGC 4697) 

@@

In Section \ref{sec:disc} we discuss our results in terms of galaxy evolution 
and we present the location of ellicular galaxies, relative to other galaxies, in the Hubble grid.

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{discmodel.eps}
\caption{Illustration of the spheroid/disc decomposition of the one-dimensional surface brightness profile, $\mu$, 
the ellipticity profile, $\epsilon$, and the specific angular momentum profile, $\lambda$,
for the three prototype early-type galaxy sub-classes. 
In the flux decompositions, the spheroid (or bulge) and the disc are shown with the red and blue color, respectively. 
The left panel shows a lenticular galaxy, composed of a bulge encased in a large-scale disc. 
The right panel displays an elliptical galaxy with (an optional) nuclear stellar disc. 
The middle panel presents an early-type galaxy with an intermediate-sized disc embedded in the spheroid. 
We refer to the last case as an ellicular galaxy.}
\label{fig:model}
\end{center}
\end{figure}

\section{Intermediate-scale disc galaxies}
\label{sec:gal}
Three examples of ellicular galaxies are Mrk 1216, NGC 1332, and NGC 3115. 
In the following Sections, we present a photometric analysis of these three galaxies, 
and we compare our results with the kinematical analysis available from the literature for Mrk 1216 and NGC 3115. 
For the galaxies NGC 1332 and NGC 3115, we used $3.6~\rm \mu m$ images obtained with the InfraRed Array Camera (IRAC) 
onboard the \emph{Spitzer Space Telescope}. 
For the galaxy Mrk 1216, we used an archived Hubble Space Telescope (\emph{HST}) image  
taken with the Wide Field Camera 3 (WFC3) and the near-infrared \emph{F160W} filter ($H$-band). 
Our galaxy decomposition technique is extensively described in Savorgnan \& Graham (2015).
Briefly, the galaxy images were background-subtracted, and masks for contaminating sources were created. 
The one-dimensional Point Spread Function (PSF) was characterized using a Gaussian profile for the \emph{HST} observation 
and a \cite{moffat1969} profile for the \emph{Spitzer} observations.
We performed an isophotal analysis of the galaxies using the IRAF\footnote{IRAF 
is the Image Reduction and Analysis Facility, distributed by the National Optical Astronomy Observatory, 
which is operated by the Association of Universities for Research in Astronomy (AURA) 
under cooperative agreement with the National Science Foundation.} task {\tt ellipse}\footnote{Our analysis 
was performed before {\tt isofit} \citep{ciambur2015} was conceived or available. 
After {\tt isofit} was recently developed and implemented in IRAF, 
we employed it to re-extract the surface brightness profiles of the galaxies NGC 1332 and NGC 3115. 
We then repeated the analysis and checked that this change does not significantly alter our results. 
In fact, although {\tt isofit} provides a more accurate description of the isophotes in the presence of an inclined disc, 
the discs of NGC 1332 and NGC 3115 are relatively faint compared to the spheroidal components, 
therefore the differences between the light profile obtained with {\tt ellipse} and that obtained with {\tt isofit} 
are small for these two galaxies. } 
\citep{taskellipse}. 
The galaxy isophotes were modelled with a series of concentric ellipses, 
allowing the ellipticity, the position angle and the amplitude of the fourth harmonic to vary with radius.  
The decomposition of the surface brightness profiles was performed with software written by G. Savorgnan 
and described in Savorgnan \& Graham (2015).
We modelled the light profiles with a combination of PSF-convolved analytic functions, 
using one function per galaxy component.

\subsection{NGC 3115}
The presence of a disc in NGC 3115 is obvious due to its edge-on orientation (Figure \ref{fig:n3115}). 
Less obvious is the radial extent of this disc, if one only relies on a visual inspection of the galaxy image. 
The ellipticity profile (Figure \ref{fig:n3115}) is consistent with the presence of an intermediate-scale disc. 
Moreover, the kinematics of NGC 3115 \citep{arnold2011n3115} also disprove the presence of a large-scale disc, 
because the galaxy is rapidly rotating only within two galaxy half-light radii ($\sim 2 \times 50~\rm arcsec$), 
and the rotation significantly drops at larger radii.  
The unsharp mask of NGC 3115 (Figure \ref{fig:n3115}) betrays the presence of a faint edge-on nuclear ring, 
which can also be spotted as a small peak in the ellipticity profile 
(at semi-major axis length $R_{\rm maj} \sim 15~\rm arcsec$). 
Such rings are common in early-type galaxies \citep{michardmarchal1993}.
The spheroidal component of NGC 3115 is well described with a \cite{sersic1963} profile.
The highly inclined intermediate-scale disc is better fit with an $n<1$ S\'ersic profile 
(the S\'ersic index $n$ regulates the curvature of the S\'ersic profile) 
rather than with an exponential function, 
as explained by \cite{pastrav2013a}. 
The nuclear ring is modelled with a Gaussian function. \\
In comparison, \cite{lasker2014data} fit NGC 3115 with a bulge + disc + envelope, 
and measured a bulge half-light radius of $3.9~\rm arcsec$ and a bulge-to-total ratio of $0.12$. 
We describe this galaxy using a spheroid + intermediate-scale disc + nuclear ring, 
and obtain a spheroid half-light radius of $43.6~\rm arcsec$ and a spheroid-to-total ratio of $0.85$. 
We have used both kinematical information and ellipticity profiles, 
together with the surface brightness profile, 
to obtain a physically consistent and meaningful model.

@@

\subsection{Mrk 1216}
Although the disc in the galaxy Mrk 1216 is not immediately apparent from the image (Figure \ref{fig:m1216}), 
the velocity map \citep{yildirim2015} reveals the presence of a fast rotating component 
within three galaxy half-light radii ($\sim 3 \times 5~\rm arcsec$). 
The ellipticity profile (Figure \ref{fig:m1216}), 
which extends out to five half-light radii, indicates the presence of an intermediate-scale disc. 
In addition, a nuclear disc is identified from the change in slope of the ellipticity profile ($R_{\rm maj} \sim 1 - 2 \rm~arcsec$), 
from the unsharp mask, 
and from a clear feature in the $B4$ fourth harmonic profile (not shown here). 
We modelled the surface brightness profile of Mrk 1216 (Figure \ref{fig:m1216}) with a S\'ersic-spheroid, 
an intermediate-sized exponential-disc, and a nuclear exponential-disc.

@@

\subsubsection{NGC 1271}
\cite{walsh2015} explored a three-component decomposition for NGC 1271 
and identified the galaxy bulge with the innermost of the three components, 
having a half-light radius of $0.61~\rm arcsec$ and a bulge-to-total flux ratio of $0.23$; 
our model features a spheroid + intermediate-scale disc, 
with a spheroid half-light radius of $3.3~\rm arcsec$ and a spheroid-to-total flux ratio of $0.67$.

\subsubsection{NGC 1277}
\cite{vandenbosch2012} proposed a model for the galaxy NGC 1277 with a bulge + disc + nuclear source + envelope, 
which gives a bulge half-light radius of $0.9~\rm arcsec$ and a bulge-to-total flux ratio of $0.24$; 
our model consists of a spheroid + intermediate-scale disc + nuclear component, 
and produces a spheroid half-light radius of $6.0~\rm arcsec$ and a spheroid-to-total flux ratio of $0.79$.

\subsubsection{NGC 3377}
\cite{lasker2014data} modelled the galaxy NGC 3377 with a bulge + nuclear disc + disc + envelope, 
and obtained a bulge half-light radius of $10.1~\rm arcsec$ and a bulge-to-total flux ratio of $0.35$; 
our model with a spheroid + intermediate-scale disc + nuclear disc 
returns a spheroid half-light radius of $61.8~\rm arcsec$ and a spheroid-to-total flux ratio of $0.94$.

\subsubsection{NGC 821}
\cite{lasker2014data} decomposed the galaxy NGC 821 into a bulge + disc + envelope, 
and measured a bulge half-light radius of $3.8~\rm arcsec$ and a bulge-to-total flux ratio of $0.19$; 
our decomposition consists of a spheroid + intermediate-scale disc, 
with a spheroid half-light radius of $36.5~\rm arcsec$ and a spheroid-to-total flux ratio of $0.79$.

\subsubsection{NGC 4697}
The galaxy NGC 4697 represents an ``extreme'' case. 
\cite{lasker2014data} fit this galaxy with a bulge + nuclear source + disc + envelope, 
and obtained a bulge half-light radius of $6.3~\rm arcsec$ and a bulge-to-total flux ratio of $0.08$; 
we described NGC 4697 using a spheroid + intermediate-scale disc + nuclear disc model, 
and measured a spheroid half-light radius of $239.3~\rm arcsec$ and a spheroid-to-total flux ratio of $0.89$. \\

Past models that ``forcedly'' described ellicular galaxies using an inner bulge 
encased within a large-scale disc 
commonly required the addition of an extended envelope or halo to account for the outer portion of the spheroid. 
Such three-component models (bulge + disc + envelope) typically reduce the spheroid luminosity by a factor of $3-4$, 
and underestimate the size of the spheroid by a factor of $6-10$, 
although more ``extreme'' cases can be found.

>>>>

%\title[Non over-massive black holes in early-type galaxies]{Early-type galaxies with intermediate-scale discs and their (non over-massive) black holes}
\title[Non over-massive black holes in early-type galaxies]{Non over-massive black holes in early-type galaxies with intermediate-scale discs}

@@

\begin{abstract}
{\bf The classification ``early-type'' galaxy includes both elliptically- and lenticular-shaped galaxies. 
%with the latter composed of a spheroidal stellar system encased within a larger, but flatter, stellar disc. 
Theoretically, the spheroid-to-disc flux ratio of an early-type galaxy can assume any positive value,  
but in practice studies often consider only spheroid/disc decompositions 
in which the disc neatly dominates over the spheroid at large galaxy radii, 
creating an inner ``bulge'' as observed in most spiral galaxies. 
Here we show that decompositions in which the disc remains embedded within the spheroid, 
labelled by some as ``unphysical'',  
correctly reproduce both the photometric and kinematic properties of early-type galaxies 
%intermediate between that of elliptical and lenticular galaxies, which we refer to as \emph{ellicular} galaxies for ease of reference. 
with intermediate-scale discs. 
Intermediate-scale discs have often been confused with large-scale discs, and modelled accordingly; 
when this happens, the spheroid luminosity is considerably underestimated. 
This has recently led to some surprising conclusions, 
such as the claim that a number of galaxies with intermediate-scale discs (e.g.~Mrk 1216, NGC 1277, NGC 1271, and NGC 1332) 
host a central black hole whose mass is abnormally large compared to expectations from the (underestimated) spheroid luminosity. 
We show that when galaxies with intermediate-scale discs are correctly modelled, 
they no longer appear as extreme outliers in the (black hole mass)-(spheroid mass) diagram. 
This not only nullifies the need for invoking different evolutionary scenarios for these galaxies 
but it strengthens the significance of the observed (black hole mass)-(spheroid mass) correlation 
and confirms its importance as a fundamental ingredient for theoretical and semi-analytic models 
used to describe the coevolution of spheroids and their central supermassive black holes. }

@@

\begin{keywords}
black hole physics -- galaxies: bulges -- galaxies: elliptical and lenticular, cD -- 
galaxies: evolution -- galaxies: structure -- galaxies: individual: Mrk 1216, NGC 1271, NGC 1277, NGC 1332, NGC 4291
\end{keywords}

@@

{\bf The awareness that many early-type galaxies contain stellar discs dates back several years 
\citep{michard1984,djorgovski1985,carter1987,capaccioli1987,bender1988,bender1990,capaccioli1988,franx1989,
nieto1988,nieto1991,rixwhite1990,rixwhite1992,vandenbergh1990,scorzabender1990,scorzabender1995,
simienmichard1990,cinzanovandermarel1993,donofrio1995,graham1998fornax,scorza1998,scorzavandenbosch1998,bendersaglia1999}. 
Since then, it has been well known that 
the identification of a stellar disc in an early-type galaxy based on the galaxy's photometric properties 
is subjected to inclination effects. 
This problem has been overcome with kinematic analysis (e.g.~the ATLAS$^{\rm 3D}$ survey, \citealt{cappellari2011}), 
which allows one to determine the presence of a rotationally-supported component in a galaxy 
in a way that can be nearly insensitive to projection effects \citep{cappellari2007,emsellem2007}. 
Yet, identifying the radial extent of an early-type galaxy's disc with respect to the spheroidal component can still be subtle. 
Most early-type galaxies are classified as ``fast rotators'' \citep{atlas3dIII,scott2014}, 

@@

The exact definition of a fast rotator can be found in \cite{emsellem2007}, 
although the most recent literature (e.g.~\citealt{arnold2011n3115,romanowskyfall2012,arnold2014}) 
prefers the use of the term ``\emph{central} fast rotator'' 
to emphasize the fact that this classification pertains to the kinematic properties of a galaxy only within its half-light radius.
Thanks to their more extended kinematic maps, 
\cite{arnold2014} revealed that some of the central fast rotators continue to be fast rotating at large radii, 
whereas other central fast rotators become slow rotating in their outer regions.

@@

($\epsilon = 1 - b/a$, where $b/a$ is the ratio of minor-to-major axis length) 
and the specific angular momentum profile 
($\lambda = \langle R |V| \rangle / \langle R \sqrt{V^2 + \sigma^2} \rangle$, 
where $R$ is the semimajor-axis radius, $V$ is the mean velocity and $\sigma$ is the velocity dispersion, \citealt{emsellem2007}) 
of 
(i) a lenticular galaxy, 
comprised of a large-scale disc which dominates the light at large radii over a relatively smaller encased bulge,  
i.e.~a disc-dominated central fast rotator that continues to be fast rotating beyond one half-light radius, 
(ii) a discy elliptical galaxy \citep{kormendybender1996} 
composed of an intermediate-scale disc embedded in a relatively larger spheroid which dominates the light at large radii,
i.e.~a spheroid-dominated central fast rotator that becomes slow rotating beyond one half-light radius, and  
(iii) an elliptical galaxy with an additional nuclear stellar disc, 
i.e.~a (spheroid-dominated) slow rotator. 
This is sequence is analogue to that illustrated in Figure 2 of \cite{cappellari2011}, 
although here we emphasize the correspondence between the spheroid/disc decomposition of the surface brightness profile 
and the ``shape'' of the ellipticity (assuming that the disc inclination is not close to face-on) and specific angular momentum profiles. 

@@

While some recent studies -- well aware of this problematic -- have correctly distinguished between large- and intermediate-scale discs, 
and modelled them accordingly (e.g.~\citealt{kormendybender2012,krajnovic2013}), 
intermediate-scale discs have been missed by many galaxy modellers of late, 

@@

(e.g.~\citealt{gadotti2008,head2014,querejeta2015,mendezabreu2015}). \\
As mentioned before, a photometric analysis allows one to identify the presence and the radial extent of a disc in an early-type galaxy 
only when the disc has a certain level of inclination. 
On the other hand, a kinematic analysis has the advantage of being virtually insensitive to inclination effects, 
but cannot help one determine the radial extent of a disc if the kinematic data are limited within one half-light radius. 
Therefore, the best results are obtained when photometry and kinematics are combined together. 
In this paper we focus on the increasingly overlooked occurence of intermediate-scale discs in galaxies with directly measured black hole masses. 

@@

In Section \ref{sec:gal} we present a detailed photometric analysis of three galaxies with intermediate-scale discs (Mrk 1216, NGC 1332, and NGC 3115) 
and we briefly describe another five galaxies with intermediate-scale discs (NGC 821, NGC 1271, NGC 1277, NGC 3377, and NGC 4697) 

@@

Finally, in Section \ref{sec:disc} we discuss our results in terms of galaxy evolution. }

%There are currently two well-known types of stellar discs in galaxies.
%The first are the large-scale discs (with exponential scale lengths of a few kiloparsec)
%that dominate the light at large radii in spiral and lenticular galaxies;
%the second are the small (tens to a couple of hundred parsec) nuclear discs observed in both early- and late-type galaxies
%(e.g.~\citealt{scorzavandenbosch1998,rest2001,balcells2007,ledo2010}).
%The origin of the nuclear discs has been speculated to arise from the infall of small satellite galaxies or gas clouds.
%The origin, or at least the on-going feeding and growth, of the large-scale discs has been attributed to cold gas flows,
%gas rich mergers and halo accretion events
%(e.g.~\citealt{whiterees1978,whitefrenk1991,navarrobenz1991,barneshernquist1992,khochfarsilk2006,dekel2009nat,ceverino2010,
%ceverino2012,conselice2012,rubin2012,martini2013,ueda2014}),
%and a thorough review can be found in \citet{combes2014arX,combes2014pro}.
%On the other hand, intermediate-sized discs have not received the same level of attention
%as their nuclear and large-scale homologues and
%they have at times been labelled and rejected as ``unphysical'' when detected.
%Here we focus on the increasingly overlooked occurence of intermediate-scale discs in galaxies with directly measured black hole masses.
%We report on the photometric and kinematical signatures of these intermediate-sized stellar discs,
%and the impact they have on the (black hole mass)-to-(spheroid stellar mass) ratio
%which is used to constrain galaxy evolution models. \\
%The majority of stellar discs have some level of inclination with respect to our line-of-sight,
%and this makes them appear elliptical (rather than round) when seen in projection on the sky.
%This can help one distinguish them from the more spherically-shaped spheroids.
%Identifying the radial extent of these discs with respect to the spheroid can however be subtle.
%Two-dimensional kinematic maps represent an important diagnostic tool for this purpose.
%Most early-type galaxies are classified as ``central fast rotators'' \citep{franx1989,atlas3dIII,scott2014},
%that is, they are rapidly rotating within their half-light radius.  
%However, more extended kinematic maps \citep{arnold2014} reveal that 
%some of the central fast rotators continue to be fast rotating at large radii, 
%whereas other central fast rotators become slow rotators in their outer regions.
%A specific angular momentum profile that is rapidly increasing beyond 1--2 half-light radii 
%is a signature of a large-scale disc, 
%while a specific angular momentum profile that increases up to 1--2 half-light radii and then declines beyond that point 
%indicates the presence of an intermediate-scale disc that no longer dominates at large radii. 
%Unfortunately, such extended kinematic maps are not yet available for large numbers of galaxies in the local Universe. 
%Nevertheless, the ellipticity profile of a galaxy's isophotes can help identify the extent of stellar discs in early-type galaxies. \\
%Building on the investigation of \cite{rixwhite1990}, 
%the toy model shown in Figure \ref{fig:model} illustrates the typical ellipticity profile 
%($\epsilon = 1 - b/a$, where $b/a$ is the ratio of minor-to-major axis length) of 
%(i) a disc-dominated early-type galaxy, 
%comprised of a large-scale disc which dominates the light at large radii over a relatively smaller encased bulge, 
%(ii) a spehroid-dominated early-type galaxy with an additional nuclear stellar disc, 
%and (iii) an early-type galaxy composed of an intermediate-scale disc embedded in a relatively larger spheroid 
%which dominates the light at large radii. 
%In general, stellar discs are intrinsically flat and circular; 
%their ellipticity, dictated by their inclination to our line of sight, is fixed. 
%Spheroids are often rounder than the observed projection on the sky of their associated discs, 
%thus their average ellipticity is often lower than that of their disc. 
%An ellipticity profile that increases with radius can be ascribed to an inclined disc that becomes progressively more important at large radii, 
%whereas a radial decrease of ellipticity signifies the opposite case. 
%This approach can be taken to the next level by inspecting the isophotes for discy structures and checking the velocity line profiles for asymmetry 
%(e.g.~\citealt{scorzabender1995} and references therein; \citealt{scorza1998}). \\
%The awareness that many so-called ``elliptical'' galaxies actually contain stellar discs 
%dates back many years 
%\citep{michard1984,djorgovski1985,carter1987,capaccioli1987,capaccioli1988,franx1989,nieto1988,nieto1991,rixwhite1990,rixwhite1992,
%vandenbergh1990,bender1990,scorzabender1990,scorzabender1995,
%simienmichard1990,cinzanovandermarel1993,donofrio1995,graham1998fornax,scorza1998,scorzavandenbosch1998,bendersaglia1999} and, 
%more recently, intermediate-scale discs were anything but unfamiliar to \cite{kormendybender2012} and \cite{krajnovic2013etal}. 
%However, intermediate-scale discs have been missed by many galaxy modellers of late, 
%who have labelled as ``unphysical'' \citep{allen2006} those spheroid/disc decompositions in which the disc does not dominate over the spheroid at large radii 
%as is observed with spiral galaxies. 
%Indeed, \citeauthor{graham2011} (\citeyear{graham2011}, his Figure 7) warned about such erroneous fits to spiral galaxies. 
%This bias has led to the rejection of many early-type galaxy decompositions similar to that illustrated in the middle panel of Figure \ref{fig:model}. 
%Unsurprisingly, studies affected by this bias have not obtained spheroid/disc decompositions with a spheroid-to-total ratio larger than $0.6 - 0.8$ 
%(e.g.~\citealt{gadotti2008,head2014,querejeta2015,mendezabreu2015}).
%In this paper we investigate the influence this has had on research pertaining to supermassive black hole mass scaling relations involving the host spheroid. \\
%This paper is structured as follows.
%In Section \ref{sec:gal} we present a detailed photometric analysis of three galaxies with intermediate-scale discs (Mrk 1216, NGC 1332, and NGC 3115)
%and we briefly describe another five galaxies with intermediate-scale discs (NGC 821, NGC 1271, NGC 1277, NGC 3377, and NGC 4697)
%already modelled by us elsewhere in the literature.
%We compare our photometric analysis with the kinematical information available from the literature,
%and explain the differences between our galaxy models and past decompositions.
%In Section \ref{sec:mm} we explore the important implications this has for the (black hole mass)-(spheroid stellar mass) diagram.
%Finally, in Section \ref{sec:disc} we discuss our results in terms of galaxy evolution.
%%and we present the location of ellicular galaxies, relative to other galaxies, in the Hubble grid.

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{discmodel.eps}
\caption{Illustration of the spheroid/disc decomposition of the one-dimensional surface brightness profile, $\mu$, 
the ellipticity profile, $\epsilon$, and the specific angular momentum profile, $\lambda$,
for the three prototype early-type galaxy sub-classes. 
In the flux decompositions, the spheroid (or bulge) and the disc are shown with the red and blue color, respectively. 
The left panel shows a disc-dominated central fast rotator (lenticular galaxy), composed of a bulge encased in a large-scale disc. 
The right panel displays a spheroid-dominated slow rotator (elliptical) with (an optional) nuclear stellar disc. 
The middle panel presents a spheroid-dominated central fast rotator (discy elliptical) with an intermediate-sized disc embedded in the spheroid. }
\label{fig:model}
\end{center}
\end{figure}

\section{Intermediate-scale disc galaxies}
\label{sec:gal}
Three examples of galaxies with intermediate-scale discs are Mrk 1216, NGC 1332, and NGC 3115. 
In the following Sections, we present a photometric analysis of these three galaxies, 
and we compare our results with the kinematical analysis available from the literature for Mrk 1216 and NGC 3115. 
For the galaxies NGC 1332 and NGC 3115, we used $3.6~\rm \mu m$ images obtained with the InfraRed Array Camera (IRAC) 
onboard the \emph{Spitzer Space Telescope}. 
For the galaxy Mrk 1216, we used an archived Hubble Space Telescope (\emph{HST}) image  
taken with the Wide Field Camera 3 (WFC3) and the near-infrared \emph{F160W} filter ($H$-band). 
Our galaxy decomposition technique is extensively described in Savorgnan \& Graham (2015).
Briefly, the galaxy images were background-subtracted, and masks for contaminating sources were created. 
The one-dimensional Point Spread Function (PSF) was characterized using a Gaussian profile for the \emph{HST} observation 
and a \cite{moffat1969} profile for the \emph{Spitzer} observations.
We performed an isophotal analysis of the galaxies using the IRAF\footnote{IRAF 
is the Image Reduction and Analysis Facility, distributed by the National Optical Astronomy Observatory, 
which is operated by the Association of Universities for Research in Astronomy (AURA) 
under cooperative agreement with the National Science Foundation.} task {\tt ellipse}\footnote{Our analysis 
was performed before {\tt isofit} \citep{ciambur2015} was conceived or available. 
After {\tt isofit} was recently developed and implemented in IRAF, 
we employed it to re-extract the surface brightness profiles of the galaxies NGC 1332 and NGC 3115. 
We then repeated the analysis and checked that this change does not significantly alter our results. 
In fact, although {\tt isofit} provides a more accurate description of the isophotes in the presence of an inclined disc, 
the discs of NGC 1332 and NGC 3115 are relatively faint compared to the spheroidal components, 
therefore the differences between the light profile obtained with {\tt ellipse} and that obtained with {\tt isofit} 
are small for these two galaxies. } 
\citep{taskellipse}. 
The galaxy isophotes were modelled with a series of concentric ellipses, 
allowing the ellipticity, the position angle and the amplitude of the fourth harmonic to vary with radius.  
The decomposition of the surface brightness profiles was performed with software written by G. Savorgnan 
and described in Savorgnan \& Graham (2015).
We modelled the light profiles with a combination of PSF-convolved analytic functions, 
using one function per galaxy component.

\subsection{NGC 3115}
The presence of a disc in the {\bf central fast rotator} NGC 3115 is obvious due to its edge-on orientation (Figure \ref{fig:n3115}). 
Less obvious is the radial extent of this disc, if one only relies on a visual inspection of the galaxy image. 
The ellipticity profile (Figure \ref{fig:n3115}) is consistent with the presence of an intermediate-scale disc. 
Moreover, the kinematics of NGC 3115 \citep{arnold2011n3115} also disprove the presence of a large-scale disc, 
because the galaxy is rapidly rotating only within two galaxy half-light radii ($\sim 2 \times 50~\rm arcsec$), 
and the rotation significantly drops at larger radii.  
The unsharp mask of NGC 3115 (Figure \ref{fig:n3115}) betrays the presence of a faint edge-on nuclear ring, 
which can also be spotted as a small peak in the ellipticity profile 
(at semi-major axis length $R_{\rm maj} \sim 15~\rm arcsec$). 
Such rings are common in early-type galaxies \citep{michardmarchal1993}.
The spheroidal component of NGC 3115 is well described with a \cite{sersic1963} profile.
The highly inclined intermediate-scale disc is better fit with an $n<1$ S\'ersic profile 
(the S\'ersic index $n$ regulates the curvature of the S\'ersic profile) 
rather than with an exponential function, 
as explained by \cite{pastrav2013a}. 
The nuclear ring is modelled with a Gaussian function. \\
In comparison, \cite{lasker2014data} fit NGC 3115 with a bulge + disc + envelope, 
and measured a bulge half-light radius of $3.9~\rm arcsec$ and a bulge-to-total ratio of $0.12$. 
We describe this galaxy using a spheroid + intermediate-scale disc + nuclear ring, 
and obtain a spheroid half-light radius of $43.6~\rm arcsec$ and a spheroid-to-total ratio of $0.85$. 
We have used both kinematical information and ellipticity profiles, 
together with the surface brightness profile, 
to obtain a physically consistent and meaningful model.

@@

\subsection{Mrk 1216}
Although the disc in the {\bf central fast rotator} Mrk 1216 is not immediately apparent from the image (Figure \ref{fig:m1216}), 
the velocity map \citep{yildirim2015} reveals the presence of a fast rotating component 
within three galaxy half-light radii ($\sim 3 \times 5~\rm arcsec$). 
The ellipticity profile (Figure \ref{fig:m1216}), 
which extends out to five half-light radii, indicates the presence of an intermediate-scale disc. 
In addition, a nuclear disc is identified from the change in slope of the ellipticity profile ($R_{\rm maj} \sim 1 - 2 \rm~arcsec$), 
from the unsharp mask, 
and from a clear feature in the $B4$ fourth harmonic profile (not shown here). 
We modelled the surface brightness profile of Mrk 1216 (Figure \ref{fig:m1216}) with a S\'ersic-spheroid, 
an intermediate-sized exponential-disc, and a nuclear exponential-disc.

@@

\subsubsection{NGC 1271}
\cite{walsh2015} explored a three-component decomposition for the {\bf central fast rotator} NGC 1271 
and identified the galaxy bulge with the innermost of the three components, 
having a half-light radius of $0.61~\rm arcsec$ and a bulge-to-total flux ratio of $0.23$; 
our model features a spheroid + intermediate-scale disc, 
with a spheroid half-light radius of $3.3~\rm arcsec$ and a spheroid-to-total flux ratio of $0.67$.

\subsubsection{NGC 1277}
\cite{vandenbosch2012} proposed a model for the {\bf central fast rotator} NGC 1277 with a bulge + disc + nuclear source + envelope, 
which gives a bulge half-light radius of $0.9~\rm arcsec$ and a bulge-to-total flux ratio of $0.24$; 
our model consists of a spheroid + intermediate-scale disc + nuclear component, 
and produces a spheroid half-light radius of $6.0~\rm arcsec$ and a spheroid-to-total flux ratio of $0.79$.

\subsubsection{NGC 3377}
\cite{lasker2014data} modelled the {\bf central fast rotator} NGC 3377 with a bulge + nuclear disc + disc + envelope, 
and obtained a bulge half-light radius of $10.1~\rm arcsec$ and a bulge-to-total flux ratio of $0.35$; 
our model with a spheroid + intermediate-scale disc + nuclear disc 
returns a spheroid half-light radius of $61.8~\rm arcsec$ and a spheroid-to-total flux ratio of $0.94$.

\subsubsection{NGC 821}
\cite{lasker2014data} decomposed the {\bf central fast rotator} NGC 821 into a bulge + disc + envelope, 
and measured a bulge half-light radius of $3.8~\rm arcsec$ and a bulge-to-total flux ratio of $0.19$; 
our decomposition consists of a spheroid + intermediate-scale disc, 
with a spheroid half-light radius of $36.5~\rm arcsec$ and a spheroid-to-total flux ratio of $0.79$.

\subsubsection{NGC 4697}
The {\bf central fast rotator} NGC 4697 represents an ``extreme'' case. 
\cite{lasker2014data} fit this galaxy with a bulge + nuclear source + disc + envelope, 
and obtained a bulge half-light radius of $6.3~\rm arcsec$ and a bulge-to-total flux ratio of $0.08$; 
we described NGC 4697 using a spheroid + intermediate-scale disc + nuclear disc model, 
and measured a spheroid half-light radius of $239.3~\rm arcsec$ and a spheroid-to-total flux ratio of $0.89$. \\
